RAS2012: Competition Entry

### 2012-07-27 ras2012-paper/src/main/latex/paper/paper.tex
Tidying in TEX files.

Following are appendixes where we provide statistics of the best available resolved systems and examples of their visualizations. The paper would be complete even without them, for which reason we believe they shouldn't be counted toward the 10-page limit.

@@

\section{Visualizations}

\begin{figure}
\centering
\includegraphics[width=190mm,angle=90]{solution.png}
\caption{RAS DATA SET TOY example territory. Undirected graph, arcs have descriptions.}
\end{figure}

\begin{figure}
\includegraphics[width=190mm,angle=90]{B1.png}
\centering
\caption{RAS DATA SET TOY example, route of Train B1. Directed graph where green marks the origin, red the destination and blue is where the train is allowed to wait.}
\end{figure}

In this section, we show examples of visualizations that the solution is capable of providing. These visualizations have been rendered on the fly using the JUNG library\footnote{Java Universal Network/Graph framework, http://jung.sourceforge.net}.

>>>>

Following are appendixes where we provide statistics of the best available resolved systems. The paper would be complete even without them, for which reason we believe they shouldn't be counted toward the 10-page limit.

@@
